Inpainting with controlled dimensionality reduction in the Fourier domain

### 2011-06-21 project/Paper/paper.tex
Paper: Outline of results completed.

\section{Results}
We compared our algorithm with the following three baseline algorithms (see figure \ref{baseline_algorithms}):
\begin{enumerate}
\item Vertical and horizontal linear interpolation,
\item Matching pursuit~\cite{matchingpursuit93} with an overcomplete dictionary of discrete cosines and
\item Gaussian interpolation as described in section \ref{gaussian_interpolation}.
\end{enumerate}

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{images/framing_artifacts.png}
\caption{Comparison with baseline algorithms for various fractions of missing pixels.}
\label{baseline_algorithms}
\end{figure}

We tested our algorithm and the two baselines on a set of natural images and further on a set of artificially created ones. 
For evaluation, we tested these algorithms with different levels of missing pixels from 0 to 100\% in 5\% steps.

Organize the results section based on the sequence of table and
figures you include. Prepare the tables and figures as soon as all
the data are analyzed and arrange them in the sequence that best
presents your findings in a logical way. A good strategy is to note,
on a draft of each table or figure, the one or two key results you
want to address in the text portion of the results.

When reporting computational or measurement results, always
report the mean (average value) along with a measure of variablility
(standard deviation(s) or standard error of the mean). ((( TODO !!! )))

@@

\section{Discussion}
Our algorithm is resistant to high percentages of missing pixels, the average error per missing pixel rises only slowly until ((( TODO level))).

Discuss the strengths and weaknesses of your approach, based on the results. Point out the implications of your novel idea on the application concerned. (((( TODO ))))

>>>>

\section{Results}
We compared our algorithm with the following three baseline algorithms (see figure \ref{baseline_algorithms}):
\begin{enumerate}
\item Vertical and horizontal linear interpolation,
\item Gaussian interpolation as described in section \ref{gaussian_interpolation} and
\item Matching pursuit~\cite{matchingpursuit93} with an overcomplete dictionary of discrete cosines.
\end{enumerate}

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{images/framing_artifacts.png}
\caption{Baseline algorithms for various fractions of missing pixels.}
\label{baseline_algorithms}
\end{figure}

We evaluated the baseline algorithms with the same sample images as optimization. With 60\% missing pixels, the algorithms had the following errors and standard deviations:

\begin{table}[h]
\centering
\begin{tabular}{l|r|r}
Algorithm & Error & Deviation \\
\hline
Linear interpolation & ? & ? \\
Gaussian interpolation & ? & ? \\
Matching pursuit & ? & ? \\
\end{tabular}
\end{table}

Since our algorithm did not perform equally well for all sample images, we print those for which it worked best and worst as figures \ref{best_image} and \ref{worst_image}.

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{images/framing_artifacts.png}
\caption{Best image with error ? and standard deviation ?.}
\label{best_image}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{images/framing_artifacts.png}
\caption{Worst image with error ? and standard deviation ?.}
\label{worst_image}
\end{figure}

The strength of our method is definitely in reconstructing edges, which can be seen in figure \ref{edge_reconstruction}.

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{images/framing_artifacts.png}
\caption{Original image with mask (left) and its reconstruciton (right).}
\label{edge_reconstruction}
\end{figure}

@@

\section{Discussion}
Discuss the strengths and weaknesses of your approach, based on the results. Point out the implications of your novel idea on the application concerned.
